Software Citation Principles

### 2016-07-14 sc-principles/software-citation-principles.tex
work using software -> research using software, re: reviewer 2 comment 7
past tense for FORCE2016 activities, re: R1 #6-7 and R2 #6

The group gathered members (see Appendix~\ref{app:wg_members}) in April and May 2015,
and then began work in June, with a number of meetings
and some off-line work by group members to gather materials documenting existing
practices in member disciplines; gather materials from workshops and other reports;
review those materials, identifying overlaps and differences; and subsequently draft this resulting document,
which will be presented and discussed at the Force2016 Conference~\cite{force2016}
in April 2016.  We expect that this discussion may lead to a second, final version, and we also
plan to have a follow-on working group that will work with stakeholders to ensure that
these principles impact the research process.

@@

\item ``Funder'' is a group that funds software or work using software.

>>>>

The group gathered members (see Appendix~\ref{app:wg_members}) in April and May 2015,
and then began work in June, with a number of meetings
and some off-line work by group members to gather materials documenting existing
practices in member disciplines; gather materials from workshops and other reports;
review those materials, identifying overlaps and differences; and subsequently draft this resulting document,
which was presented and discussed at the Force2016 Conference~\cite{force2016}
in April 2016.  This discussion led to a second, final version, and we also
plan to have a follow-on working group that will work with stakeholders to ensure that
these principles impact the research process.

@@

\item ``Funder'' is a group that funds software or research using software.
